---
title: "Lab 8 Submission"
author: "Rui Gao"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1908) 
```

# Instructions

Complete the lab tutorial before completing this file.  Use the R Markdown version of this file to complete and submit your homework.  Items in **bold** require an answer. Make sure you change the author in the header to your own name. 

1\. **Use `rep()` to generate a vector containing: 0, 0, 0, 0, 0, 1, 1, 1, 2, 2**
```{r}
x_1 <- c(rep(0,5),rep(1,3),rep(2,2))
```


2\. **In your own words, describe what happens when negative numbers are used in 
square bracket subsetting**. *You may refer to the example below.*

```{r}
x <- c("a", "b", "c", "d", "e")
x[c(-2, -4)]
```
The vector of x has deleted the elements inside as the order number we inputted.

3\. The last function presented in the lab is as follows:

```{r}
perm_tstat <- function(x, n1){
  n <- length(x)
  grp1_indices <- sample(1:n, size = n1, replace = FALSE)
  grp1_perm <- x[grp1_indices] 
  grp2_perm <- x[-grp1_indices] 
  t.test(grp1_perm, grp2_perm)$statistic
}
```

**Describe how you would edit this function to use the difference in sample means, instead
of the t-statistic, as the test statistic in the permutation test.**

"statistic" in t.test would be changed into "estimate". Then extract value of "mean of x and y", do a minus between them and saved into a new variable.


