---
title: "Lab 1"
author: "Rui Gao"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
# This ensures all your code chunks are displayed in your document
knitr::opts_chunk$set(echo = TRUE)
```

Questions that you need to answer are in **bold**.  Add your answers in the spaces provided, you may delete any blanks, ___, but do not delete the question text.  

The sections of this lab match those in the [Programming Basics primer](https://rstudio.cloud/learn/primers/1.2) on Rstudio Cloud, so you might like to tackle them as you work through the primer.  

## Functions

**Use the `exp()` function, to find the exponential of 10**.
```{r}
exp(10)
```

**How would you open the help page for the `exp()` function**?
```{r, eval = FALSE}
?exp()
```

## Arguments

Consider the code in the following chunk:
```{r}
round(3.141593, digits = 2)
```
**How many arguments are being passed to `round()`?** ___ 2 arguments

**What is the name of the argument that is being passed the value 3.141593?** ___ it's been called "x" in default.

## Objects

This code generates a sequence of values from 0 to 1 in steps of 0.05.
```{r}
steps <- seq(0, 1, 0.05)
length(steps)
```
**Edit the chunk above to: save the values to an object called `steps`, then use the `length()` function to find the length of `steps`.** 

## Vectors

Consider the vector `catfood_servings`:
```{r}
catfood_servings <- c(Scylla = 3, Dexter = 5, Underfloor = 4)
```

**Extract the 2nd element of `catfood_servings`.**
```{r}
catfood_servings[2]
```

**Extract the element with the name `Dexter`**
```{r}
catfood_servings["Dexter"]

```


## Types

```{r}
heights <- c("172", "167", "96", "202", "150")
names <- c("Luke Skywalker", "C-3PO", "R2-D2", "Darth Vader", "Leia Organa")
humans <- c(TRUE, FALSE, FALSE, TRUE, TRUE)
```

**What type of object is `heights`?** ___ char

**What type of object is `names`?** ___ char

**What type of object is `humans`?** ___ bool

