---
title: "Lab 4 Submission"
author: "Rui Gao"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions

Complete the lab tutorial before completing this file.  Use the R Markdown version of this file to complete and submit your homework.  Items in **bold** require an answer. Make sure you change the author in the header to your own name. 

The following three lines are taken from the lab tutorial:
```{r, eval = FALSE}
Z <- (mean(x) - 2.5) / (sd(x)/sqrt(length(x)))
2 * pnorm(abs(Z), mean = 0, sd = 1, lower.tail = FALSE)
mean(x) - qnorm(0.975) * sd(x)/sqrt(length(x))
```

Consider the following six components seen in this code:

* `mean(x)`
* `2.5`
* `sd(x)`
* `length(x)`
* `qnorm(0.975)`
* `sd(x) / sqrt(length(x))`

**For each of the six components, match it to the corresponding notation and description from the following lists**.

Mathematical notation (these are written using LaTeX notation, you may need to 
Knit to preview them:

* $\text{SE}_{\overline{x}}$           is sd(x)/sqrt(length(x))
* $\overline{x}$                       is mean(x)
* $s$                                  is sd(x)
* $z_{\alpha/2}$ for $\alpha = 0.05$   is qnorm(0.975)
* $n$                                  is length(x)
* $\mu_0$                              is 2.5

Description:

* population mean under the null hypothesis is 2.5
* sample size is length(x)
* critical value for an $\alpha = 0.05$ level Z-test is qnorm(0.975)
* sample standard deviation is sd(x)
* standard error of the mean is sd(x)/sqrt(length(x))
* sample average is mean(x)
