---
title: "Lab 5 Submission"
author: "Rui Gao"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1908) 
x <- rnorm(n = 40, mean = 5, sd = 5) 
```

# Instructions

Complete the lab tutorial before completing this file.  Use the R Markdown version of this file to complete and submit your homework.  Items in **bold** require an answer. Make sure you change the author in the header to your own name. 

1.  All three test functions (`t.test()`, `binom.test()` and `prop.test()`) have an argument called `alternative`. **What does this argument do?** Use the help to find out.
  Using it to clarify that what kind of test are we doing, one side or two side? If it's one side, the left or the right?


2.  In the `t.test()` section of the lab, you tested the hypotheses:
    $$
    H_{0}: \mu = 3, \quad H_{A}: \mu \neq 3 
    $$
    
    **Edit the code below to test the hypotheses:**
    $$
    H_{0}: \mu = 5, \quad H_{A}: \mu > 5 
    $$
    
    ```{r, results = "hide"}
    t.test(x, mu = 5, alternative = c ("greater"), conf.level = 0.95)
    ```


3. In the `prop.test()` section of the lab, you tested the hypotheses:
    
    $$ 
    H_{0}: p = 0.25, \quad H_{A}: p \neq 0.25 
    $$
    based on observing 20 successes in 100 trials.
    
    **Edit the code below to test the same hypotheses, but based 
    on 200 successes in 1000 trials:**
    
    ```{r, results = "hide"}
    prop.test(x = 200, n = 1000, p = 0.25, 
      conf.level = 0.95, correct = FALSE)
    ```

4.  In the `prop.test()` section of the lab, you tested the hypotheses:
    
    $$ 
    H_{0}: p = 0.25, \quad H_{A}: p \neq 0.25 
    $$
    based on observing 20 successes in 100 trials.
    
    **Edit the code below to test the same hypotheses, with the same data,  but using an exact Binomial test instead. Would you reach the same conclusion?**

    ```{r, results = "hide"}
    prop.test(x = 20, n = 100, p = 0.25, 
      conf.level = 0.95, correct = FALSE)
    ```
    ```{r, results = "hide"}
    binom.test(x = 20, n = 100, p = 0.25, 
      conf.level = 0.95)
    ```
    Yes, in this case, we have the same conclusion that we would fail to reject the H_0. 
