---
title: "Lab 3 Submission"
author: "Rui Gao"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions

Complete the lab tutorial before completing this file.  Use the R Markdown version of this file to complete and submit your homework.  Items in **bold** require an answer. Make sure you change the author in the header to your own name. 


1. Consider the following code:
    ```{r, eval = FALSE}
    many_sample_means <- replicate(10, 
      mean(rgamma(n = 5, shape = 1, rate = 5)))
    ```
    
    **Fill in the blanks**: This code simulates _10__ values from the sampling distribution 
of the sample mean for samples of size _5__ from a Gamma( _1__ , _5__ ) distribution.

2. **Fill in the blanks** For a Gamma(5, 1) population (the same population as in the lab tutorial), the Central Limit Theorem predicts the sampling distribution of the sample mean for samples of size 100 is approximately Normal with mean __5_ and variance _0.05__.
  
3. In the lab you compared histograms of the sampling distribution of the sample mean with increasing sample sizes (10, 50, and 100).  **If the Central Limit Theorem applies, 
what should you observe about the histograms as the sample size increases?**

  They have the same center, but as the number of size increases, the bell gets more and more narrow.